Dike experiment

### 2023-01-25 manuscript.Rmd
Update manuscript.Rmd

A non-metric multidimensional scaling ordination (NMDS) with Jaccard dissimilarity was used to visualize variation in species composition in space and time. Rare species with an accumulated cover over all plots of less than 0.5% were excluded (2D-stress: 0.21).

@@

The posterior distributions shown in the interactions plots which separates exposition and survey year is less clear. <!--# Go on here -->

@@

```{r figure-persistence, fig.cap = "Persistence"}
#knitr::include_graphics(here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x14cm.tiff"))
```

@@

```{r figure-fcs, fig.cap = "Favourable Conservation Status (FCS)"}
#knitr::include_graphics(here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x14cm.tiff"))
```

@@

```{r figure-recovery, fig.cap = "Recovery"}
#knitr::include_graphics(here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x14cm.tiff"))
```

>>>>

A non-metric multidimensional scaling ordination (NMDS) with Jaccard dissimilarity was used to visualize variation in species composition in space and time. Seven species which had an accumulated cover over all plots of less than 0.5% were excluded (2D-stress: 0.21).

@@

The posterior distributions which are shown in the interactions plots which separates exposition and survey year indicate for all three responses a strong positive development after one year with slow increase in following years (Figures \@ref(fig:figure-persistence); \@ref(fig:figure-fcs); \@ref(fig:figure-recovery)) . Both expositions have similar trends but for all responses the values are clearly lower on the south exposition. Persistence values are more than 50% higher on the north exposition (Figure \@ref(fig:figure-persistence)). The effect of restoration treatments is in the interaction plots not clear. Hay meadow seed mixture led to a closer development to hay meadow references and almost reached on the north exposition the area of the standard deviation of reference sites (Figure \@ref(fig:figure-recovery)). Though, the sand admixture had no clear effect on the development. Persistence of both seed mixture types seems to be slightly positive affected by sand admixture on the north exposition (Figure \@ref(fig:figure-persistence)).

<!--# Go on here -->

@@

```{r figure-persistence, fig.cap = "Persistence"}
knitr::include_graphics(here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x14cm.tiff"))
```

@@

```{r figure-fcs, fig.cap = "Favourable Conservation Status (FCS)"}
knitr::include_graphics(here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x14cm.tiff"))
```

@@

```{r figure-recovery, fig.cap = "Recovery"}
knitr::include_graphics(here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x14cm.tiff"))
```
